%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Meta (Formerly Facebook)} % Organisation
    {Menlo Park, CA} % Location
    {Jun 2022 - Aug 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Sped up audio processing model inference on embedded devices by 300\% via multithreading.}
        \item {Joint inventor for patent application.}
        \item {Collaborated with research team, and provided valuable feedback on model performance.}
        \item {Integrated model inference in RTC audio pipeline. Moved slow code in Android's Java layer to native C++.}
        \item {Developed UI for switching model and audio pipeline parameters for quick real-world testing and rapid feedback on performace.}
        \item {Fixed bugs in PyTorch codebase for compilation of operators for ARM devices.}
        \item {\textbf{Technical Skills:} PyTorch, C++, Java, Kotlin, Android, Linux, Mercurial}
        \item {\textbf{Soft Skills:} Synthesis and presentation of results, Communication and collaboration with multiple engineering and research teams.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Facebook} % Organisation
    {Remote} % Location
    {Jul 2021 - Aug 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed back-end for transfer learning for model parameters with sparse and dense features.}
        \item {Created algorithm that improved matching of features from $O(n^2)$ to $O(n\log(n))$.}
        \item {Worked with data scientists to improve performance of personalization models.}
        \item {\textbf{Technical Skills:} Python, Caffe2, Linux, Mercurial}
        \item {\textbf{Soft Skills:} Proactive communication with data scientists.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}


%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Other Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {UABC Experimental Rocketry Team "CIUDSE"} % Organisation
    {Lead Systems Engineer} % Project
    {} % Location
    {Oct 2022 - Jun 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Organization and management of multiple engineering teams for "CIMARRON III", a 10k AGL mission for Spaceport America Cup 2023}
        \item {Engineering of complete rocket system: airframe, recovery, propulsion, avionics, and payload.}
        \item {Preparation of technical reports and presentations.}
        \item {Development of real-time video transmission payload and directional tracking ground station for live-streaming from the rocket during flight.}
        \item {\textbf{Technical Skills:} SolidWorks, MATLAB, LaTeX, Rust, Python}
        \item {\textbf{Soft Skills:} Leadership, Resource management, Communication with multidisciplinary teams, Teamwork, Presentation skills, Report writing}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {UABC Experimental Rocketry Team "CIUDSE"} % Organisation
  {Ground Station Lead} % Project
  {} % Location
  {Feb 2021 - Sep 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of project
      \item {Developed a telemetry server from scratch with time-series database integration for real-time and historical queries.}
      \item {Designed and assembled telecommunications hardware for reliable, long-range, real-time telemetry from the rocket.}
      \item {Telecomunications protocol firmware for rocket flight computer and ground station.}
      \item {Development of real-time video transmission payload  and directional tracking ground station for live-streaming   from the rocket during flight.}
      \item {Development of front end for visualization of real-time and historical telemetry based on NASA's OpenMCT.}
      \item {Development of plug-in for visualization of geodetic data on a 3D Earth representation or on a 2D map, integrating with telemetry from OpenMCT.}
      \item {\textbf{Technical Skills:} STM32, ESP32, GPS, C, C++, Python, JavaScript}
      \item {\textbf{Soft Skills:} Leadership, Teamwork, Presentation skills, Technical report writing}
    \end{cvitems}
  }


%---------------------------------------------------------
  \cventry
    {CNyN Programming Club \& ICPC Team} % Organisation
    {Team Captain} % Project
    {} % Location
    {Aug 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Founded programming club in our faculty}
        \item {Lead the initive to establish the first official ICPC competition site of Baja California in our faculty.}
        \item {Coached 4 teams for 2022 ICPC season.}
        \item {ICPC Mexico finalist in 2020, 2021, ans 2022 seasons.}
        \item {\textbf{Technical Skills:} C++, Python, Algorithms, Data Structures}
        \item {\textbf{Soft Skills:} Leadership, Teaching, Preparation of didactic material.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {"Cassiopeia" Rover Team} % Project
    {Software Lead} % Organisation
    {} % Location
    {Feb 2019 - Feb 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {2nd place in national rover competition "HUBL 2019"}
        \item {Development of firmware for control of drivetrain and control of rock manipulating arm.}
        %\item {Design and simulation of mechanical linkages.}
        \item {Design and construction of actuated camera for remote control view panning.}
        %\item {Design and implementation of communication protocol between microcontroller and main mission planning computer.}
        \item {Development of optimized video pipeline with GStreamer for low latency video transmission, using Jetson Nano and WiFi.}
        \item {Development of remote control interface with telemetry visualization, video link and real-time control via a WiiMote.}
        \item {\textbf{Technical Skills:} C++, ROS, Linux, GStreamer, OpenCV, Arduino, UART, I2C, WiFi, Bluetooth}
        %\item {\textbf{Soft Skills:} Report writing, Logical Thinking, Critical Thinking.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
