%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {Ignition4 Flight Computer} % Organisation
  {} % Project
  {} % Location
  {2022 - 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of project
      \item {Designed and fabricated a flight computer for high powered rocketry. Developed software for rocket recovery, data logging, and user interface. }
      \item {Flight computer is based on ESP32-C3 microcontroller. Uses bluetooth for configuration. Includes 2 pyro channels for dual recovery.}
    \end{cvitems}
  }


%---------------------------------------------------------
  \cventry
    {Autonomous Rover with Object Recognition} % Organisation
    {} % Project
    {} % Location
    {2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Control and objective modification via web interface.}
        \item {Autonomous navigation to target object, with obstacle detection.}
        \item {OpenCV target detection, motor control, and sensor signal processing on RaspberryPi}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Warehouse Storage Optimizer} % Organisation
  {} % Project
  {} % Location
  {2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of project
      \item {Worked with manufacturer to optimize storage of inventory.}
      \item {Integrated inventory database for automatic weekly assignment of storage units.}
    \end{cvitems}
  }

%---------------------------------------------------------
  % \cventry
  % {Telegram Bot for Refugee Aid from Ukraine} % Organisation
  % {} % Project
  % {} % Location
  % {2022} % Date(s)
  % {
  %   \begin{cvitems} % Description(s) of project
  %     \item {Worked with nonprofit organization aiding refugees from Ukraine.}
  %     \item {Developed Telegram bot to increase efficiency in case procesing.}
  %   \end{cvitems}
  % }

%---------------------------------------------------------
  \cventry
  {School Schedule Optimizer} % Organisation
  {} % Project
  {} % Location
  {2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of project
      \item {Created a tool to facilitate the process of creating school schedules and balancing the students' and professors' preferences.}
      \item {Algorithm based on simulated annealing. Multithreaded implementation written in Rust. UI was made using egui library.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
  {Phonebook Format Updater} % Organisation
  {} % Project
  {} % Location
  {2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of project
      \item {In 2020, there was a change in the way Mexican mobile phone numbers were dialed. This program used the Google Contacts API to quickly update all your phonebook to the new format. Written in Python.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
  {Mancala AI} % Organisation
  {} % Project
  {} % Location
  {2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of project
      \item {A Mancala playing agent. Outperformed all online bots available on online playing platforms.}
      \item {Uses min-max search with alpha-beta prunning.}
    \end{cvitems}
  }

%---------------------------------------------------------

\end{cventries}
